### 2021-09-09 input/proposal.tex
start to seem final

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process ($S(\alpha_a) \implies
    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
    removal eventually triggers the forwarding of best delivered
    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
    \processes may deliver other stale messages that will be 
    eventually removed to never be delivered again. In the worst case,
    all processes deliver and remove all stale messages to ultimately
    deliver and forward only up-to-date messages ($\eventually d_c(m')
    \implies \neg S(m')$). As in Theorem~\ref{theo:bef}, they
    eventually deliver and forward their best up-to-date message.

>>>>

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process ($S(\alpha_a) \implies
    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
    removal eventually triggers the forwarding of best delivered
    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
    \processes may deliver other stale messages that will be 
    eventually removed to never be delivered again. In the worst case,
    all \processes deliver and remove all stale messages to ultimately
    deliver and forward only up-to-date messages ($\eventually d_c(m')
    \implies \neg S(m')$). As in Theorem~\ref{theo:bef}, they
    eventually deliver and forward their best up-to-date message.
